---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# vistributions

> Visualize probability distributions

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/vistributions)](https://cran.r-project.org/package=vistributions) [![cran checks](https://cranchecks.info/badges/summary/vistributions)](https://cran.r-project.org/web/checks/check_results_vistributions.html) [![Travis-CI Build Status](https://travis-ci.org/rsquaredacademy/vistributions.svg?branch=master)](https://travis-ci.org/rsquaredacademy/vistributions) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/vistributions?branch=master&svg=true)](https://ci.appveyor.com/project/aravindhebbali/vistributions) [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)


## Installation

```{r cran-installation, eval = FALSE}
# Install release version from CRAN
install.packages("vistributions")

# Install development version from GitHub
# install.packages("devtools")
devtools::install_github("rsquaredacademy/vistributions")
```

## Articles

- [Explore Distributions](https://vistributions.rsquaredacademy.com/articles/introduction_to_vistributions.html)

## Usage

```{r, echo=FALSE, message=FALSE}
library(vistributions)
```

### Normal Distribution

```{r normal}
# visualize normal distribution
vdist_normal_plot()

# visualize quantiles out of given probability
vdist_normal_perc(0.95, mean = 2, sd = 1.36, type = 'both')

# visualize probability from a given quantile
vdist_normal_prob(c(-1.74, 1.83), type = 'both')
```

## Getting Help

If you encounter a bug, please file a minimal reproducible example using 
[reprex](https://reprex.tidyverse.org/index.html) on github. For questions 
and clarifications, use [StackOverflow](https://stackoverflow.com/).

## Community Guidelines

Please note that the 'vistributions' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
